cpcrw_ms

### 2015-10-09 manuscript/cpcrw_manuscript.Rmd
Update cpcrw_manuscript.Rmd
Added Peyton's text to intro

@@

@@

SE slope, transition zone

@@

**Laboratory iincubation*

@@

@@

Analysis.

>>>>

The goal of this study was to characterize the chemical and biological properties of sub-Arctic, active layer soils subjected to changes in temperature and moisture. We also sought to determine the relative control temperature and moisture have on the fate of C and greenhouse gas emissions in active layer soils lying directly above permafrost. We hypothesized that the field moist 20˚C cores have a greater potential to lose C as both CO2 and CH4 than cores held at 4˚C due to increased aerobic and anaerobic microbial activity. We also hypothesized that drought-induced cores would have a higher potential to lose more ‘complex’ carbon compounds (aromatic C) as these compounds are desorbed due to increased surface tension.

@@

**Field sampling**

@@

SE slope, transition zone...

@@

**Laboratory incubation**

@@

Analysis. Outlier exclusion.

**Data and code availability**

@@
